---
title: "group8"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{group8}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Group8)
```

Link to github:
https://github.com/rforbiodatascience22/group_8_package

Description of the package:
The package is used to translate a DNA sequence into amino acids using a codon translation table. It has 5 functions.

Description of the functions:
Function 1 (clean_dna) removes every character that is not a nucleotide (A,C,G or T) from raw DNA sequence in FASTA format and deletes new lines. The input (raw_seq) is the FASTA document. Everything that are not the 4 nucleotides is removed and a new sequence is stored in clean_seq. Additionally, it removes all the blank spaces and new lines and create a vector called dna_seq that will be the output.

To use function 1:  clean_DNA = clean_dna('sequnece')

Function 2 (tforu) substitutes all "T"s of a given DNA sequence for "U"s. 

To use function 2: RNA = tforu('clean_DNA')

Function 3 (finds_codons) splits a string containing an DNA/RNA sequence into 
the individual codons.

To use function 2: codons = finds_codons('RNA')

Function 4:

Function 5: The person(s) responsible for function five, describe how you added the three packages as dependencies and included the pipe in the package namespace.

This package can be used to individual several functions described above. But when using the packages function in conjunction. A DNA fasta sequence can be turned into a....... 



Discussion about dependencies: It is important to limited the dependencies that your package have due to people using the package has download others package to make it work. 
Also the author of the package is not in control of changes of dependent packages. Sometimes dependencies can not be avoided like. An exemplar of this is when the dependencies package is is doing something which would be to time required to write yourself like ggplot. 

It is possible to import an package in two ways: 'package::function()' and '@importFrom package function'. The main difference between these to is that 'package::function()' is more explicit telling which package and function is applied.  
