---
title: "group8"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{group8}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Group8)
```

Description of the package:
The package is used to translate a DNA sequence into amino acids using a codon translation table. It has 5 functions.

Description of the functions:
Function 1 (clean_dna) removes every character that is not a nucleotide (A,C,G or T) from raw DNA sequence in FASTA format and deletes new lines. The input (raw_seq) is the FASTA document. Everything that are not the 4 nucleotides is removed and a new sequence is stored in clean_seq. Additionally, it removes all the blank spaces and new lines and create a vector called dna_seq that will be the output.

Function 2 (tforu) substitutes all "T"s of a given DNA sequence for "U"s. 
Function 5: The person(s) responsible for function five, describe how you added the three packages as dependencies and included the pipe in the package namespace.


Functions that could be added to the package: 
Discuss why it is a good idea to limit the number of dependencies your package has. When can it not be avoided?
Discuss the difference between adding an @importFrom package function tag to a function description compared to using package::function(). Read this section if you are not sure or just want to learn more.
